A Descriptive Analysis of How Psychology Journals Handle Post-Publication Critiques

### 2024-01-03 manuscript_NHB.Rmd
Minor formatting changes
removed in-text print() functions where followed by paste as this for some reason decided to stop showing in pdf knit. Whole text changed due to folder name change leading to altering wrong manuscript copy so full text copy-pasted over.

  As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "YES") / n() * 100, "%"))` of journals, and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "ARCHIVE") / n() * 100, "%"))` of journals. `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO IMPLICIT") / n() * 100, "%"))` had no advertised post-publication critique policy, and `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO EXPLICIT") / n() * 100, "%"))` of journals explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*). `r paste0(prominent2types, "%")` of journals accepted two types (commentaries and letters); *International Journal of Mental Health and Addiction*, *Journal of Environmental Psychology*, and *Psychological Science*. 
    Among the 41 explicitly stated post-publication critique options, restrictions on length were quantitatively stated (e.g., '1,000 words') in `r print(paste(prom_quantitative_length$count, "(", round(prom_quantitative_length$percentage), "%)", sep = ""))` cases, qualitatively stated (e.g. 'brief') in  `r print(paste(prom_qualitative_length$count, "(", round(prom_qualitative_length$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(prom_notStated_length$count, "(", round(prom_notStated_length$percentage), "%)", sep = ""))` cases. Time-to-submit was quantitatively stated (e.g., '4 weeks') in `r print(paste(prom_quantitative_time$count, "(", round(prom_quantitative_time$percentage), "%)", sep = ""))` cases, qualitatively stated (e.g., 'timely') in `r print(paste(prom_qualitative_time$count, "(", round(prom_qualitative_time$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(prom_notStated_time$count, "(", round(prom_notStated_time$percentage), "%)", sep = ""))` cases. Number of references allowed was quantitatively stated (e.g., 'max 20') in `r print(paste(prom_quantitative_ref$count, "(", round(prom_quantitative_ref$percentage), "%)", sep = ""))` cases and not stated in `r print(paste(prom_notStated_ref$count, "(", round(prom_notStated_ref$percentage), "%)", sep = ""))`. Whether critiques were sent for external peer-review was only stated in `r print(paste((prom_yes_review$count + prom_no_review$count), "(", round(prom_yes_review$percentage + prom_no_review$percentage), "%)", sep = ""))` cases, in `r print(paste(prom_yes_review$count, "(", round(prom_yes_review$percentage), "%)", sep = ""))` cases this was in the affirmative. 
    When stated quantitatively, length limits ranged from `r prom_length_range %>% pull(prom_min_length)` - `r prom_length_range %>% pull(prom_max_length)` words, time-to-submit limits ranged from `r prom_time_range %>% pull(prom_min_time)` -`r prom_time_range %>% pull(prom_max_time)` weeks, reference limits ranged between `r prom_ref_range %>% pull(prom_min_ref)` -`r prom_ref_range %>% pull(prom_max_ref)`. Table *XX* shows descriptive statistics for stated quantitative restrictions, broken down by critique type.

@@

  Among the 25 cases of explicitly accepted post-publication critiques, restrictions on length were quantitatively stated in `r print(paste(rand_quantitative_length$count, "(", round(rand_quantitative_length$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(rand_notStated_length$count, "(", round(rand_notStated_length$percentage), "%)", sep = ""))` cases. Time-to-submit was quantitatively stated in `r print(paste(rand_quantitative_time$count, "(", round(rand_quantitative_time$percentage), "%)", sep = ""))` case, and qualitatively stated in `r print(paste(rand_qualitative_time$count, "(", round(rand_qualitative_time$percentage), "%)", sep = ""))`, and not stated in `r print(paste(rand_notStated_time$count, "(", round(rand_notStated_time$percentage), "%)", sep = ""))` cases. Number of references allowed was stated quantitatively in `r print(paste(rand_quantitative_ref$count, "(", round(rand_quantitative_ref$percentage), "%)", sep = ""))` cases, and not stated in `r print(paste(rand_notStated_ref$count, "(", round(rand_notStated_ref$percentage), "%)", sep = ""))` cases. Whether critiques were peer-reviewed was stated in `r print(paste((rand_yes_review$count + rand_no_review$count), "(", round(rand_yes_review$percentage + rand_no_review$percentage), "%)", sep = ""))` cases, in `r print(paste(rand_yes_review$count, "(", round(rand_yes_review$percentage), "%)", sep = ""))` cases this was in the affirmative. When stated quantitatively, length limits ranged from `r rand_length_range %>% pull(rand_min_length)` - `r rand_length_range %>% pull(rand_max_length)` words, time-to-submit limits were only stated by one journal (as 9 months), references ranged between `r rand_ref_range %>% pull(rand_min_ref)` - `r rand_ref_range %>% pull(rand_max_ref)`. Table *XX* shows descriptive statistics for these restrictions, broken down by critique type.

>>>>

As shown in Figure *XX*, post-publication critique policies were explicitly stated by `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "YES") / n() * 100, "%"))` of journals, and we inferred that they were implicitly accepted (as denoted by archival examples) in `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "ARCHIVE") / n() * 100, "%"))` of journals. `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO IMPLICIT") / n() * 100, "%"))` had no advertised post-publication critique policy, and `r dj_prominent %>% filter(ppc_type == "A") %>% summarise(percentage = paste0(sum(has_ppc == "NO EXPLICIT") / n() * 100, "%"))` of journals explicitly stated that they did not accept critiques (*Clinical Psychology: Science and Practice and Psychological Bulletin*). `r paste0(prominent2types, "%")` of journals accepted two types (commentaries and letters); *International Journal of Mental Health and Addiction*, *Journal of Environmental Psychology*, and *Psychological Science*.

Among the 41 explicitly stated post-publication critique options, restrictions on length were quantitatively stated (e.g., '1,000 words') in `r paste(prom_quantitative_length$count, "(", round(prom_quantitative_length$percentage), "%)", sep = "")` cases, qualitatively stated (e.g. 'brief') in  `r paste(prom_qualitative_length$count, "(", round(prom_qualitative_length$percentage), "%)", sep = "")` cases, and not stated in `r paste(prom_notStated_length$count, "(", round(prom_notStated_length$percentage), "%)", sep = "")` cases. Time-to-submit was quantitatively stated (e.g., '4 weeks') in `r paste(prom_quantitative_time$count, "(", round(prom_quantitative_time$percentage), "%)", sep = "")` cases, qualitatively stated (e.g., 'timely') in `r paste(prom_qualitative_time$count, "(", round(prom_qualitative_time$percentage), "%)", sep = "")` cases, and not stated in `r paste(prom_notStated_time$count, "(", round(prom_notStated_time$percentage), "%)", sep = "")` cases. Number of references allowed was quantitatively stated (e.g., 'max 20') in `r paste(prom_quantitative_ref$count, "(", round(prom_quantitative_ref$percentage), "%)", sep = "")` cases and not stated in `r paste(prom_notStated_ref$count, "(", round(prom_notStated_ref$percentage), "%)", sep = "")`. Whether critiques were sent for external peer-review was only stated in `r paste((prom_yes_review$count + prom_no_review$count), "(", round(prom_yes_review$percentage + prom_no_review$percentage), "%)", sep = "")` cases, in `r paste(prom_yes_review$count, "(", round(prom_yes_review$percentage), "%)", sep = "")` cases this was in the affirmative.

When stated quantitatively, length limits ranged from `r prom_length_range %>% pull(prom_min_length)` - `r prom_length_range %>% pull(prom_max_length)` words, time-to-submit limits ranged from `r prom_time_range %>% pull(prom_min_time)` - `r prom_time_range %>% pull(prom_max_time)` weeks, reference limits ranged between `r prom_ref_range %>% pull(prom_min_ref)` -`r prom_ref_range %>% pull(prom_max_ref)`. Table *XX* shows descriptive statistics for stated quantitative restrictions, broken down by critique type.

@@

Among the 25 cases of explicitly accepted post-publication critiques, restrictions on length were quantitatively stated in `r paste(rand_quantitative_length$count, "(", round(rand_quantitative_length$percentage), "%)", sep = "")` cases, and not stated in `r paste(rand_notStated_length$count, "(", round(rand_notStated_length$percentage), "%)", sep = "")` cases. Time-to-submit was quantitatively stated in `r paste(rand_quantitative_time$count, "(", round(rand_quantitative_time$percentage), "%)", sep = "")` case, and qualitatively stated in `r paste(rand_qualitative_time$count, "(", round(rand_qualitative_time$percentage), "%)", sep = "")`, and not stated in `r paste(rand_notStated_time$count, "(", round(rand_notStated_time$percentage), "%)", sep = "")` cases. Number of references allowed was stated quantitatively in `r paste(rand_quantitative_ref$count, "(", round(rand_quantitative_ref$percentage), "%)", sep = "")` cases, and not stated in `r paste(rand_notStated_ref$count, "(", round(rand_notStated_ref$percentage), "%)", sep = "")` cases. Whether critiques were peer-reviewed was stated in `r paste((rand_yes_review$count + rand_no_review$count), "(", round(rand_yes_review$percentage + rand_no_review$percentage), "%)", sep = "")` cases, in `r paste(rand_yes_review$count, "(", round(rand_yes_review$percentage), "%)", sep = "")` cases this was in the affirmative.

When stated quantitatively, length limits ranged from `r rand_length_range %>% pull(rand_min_length)` - `r rand_length_range %>% pull(rand_max_length)` words, time-to-submit limits were only stated by one journal (as 9 months), references ranged between `r rand_ref_range %>% pull(rand_min_ref)` - `r rand_ref_range %>% pull(rand_max_ref)`. Table *XX* shows descriptive statistics for these restrictions, broken down by critique type.
